---
title: "Customers over Certain Dollar Amount"
output:
  github_document:
    html_preview: false
---
#### Clear Environment
```{r}
rm(list = ls())
```

#### Load Packages
```{r}
library(tidyverse)
library(dplyr)
library(writexl)
library(readxl)
library(stringr)
library(ggplot2)
library(dplyr)
library(lubridate)
```
#### Load Dataset 
```{r}
pi <- read_xlsx("/Users/matt/Desktop/Puffin/Projects/_Puffin_Data/220526_Posted_Sales_Invoice.xlsx")
head(pi)
```
#### Create new dataframe with filters
```{r}
df <- pi %>%
  filter(`Document Date` > "2021-01-01") %>% 
  filter(`Customer Name` != 'Shopify') %>% 
  filter(`Customer Name` != 'Shopify Orders') %>% 
  filter(Canceled == 0)
```

#### Group DataFrame by SO & Customer
- total the amount per SO
```{r}
df_grouped <- df %>%
  group_by(`Order No.`, `Customer Name`) %>%
  summarise(Total_Amt = sum(Amount)) %>%
  ungroup()
```

#### Find Customers with Avg Orders over $2k
```{r}
customers_avg_over_2k <- df_grouped %>% 
  group_by(`Customer Name`) %>% 
  summarise(Avg_Order = mean(Total_Amt),
            Num_Orders = n()) %>% 
  filter(Avg_Order >= 2000) %>% 
  ungroup()
  
```

#### Subset these customers from the original dataframe
```{r}
customers_2k <- subset(df, df$`Customer Name` %in% customers_avg_over_2k$`Customer Name`)
```

#### Determine Number of Orders Customers with $2k average have placed and compute the average per month
```{r}
customers_2k_count <- customers_2k %>% 
  group_by(`External Document No.`, `Customer Name`) %>% 
  summarise(c = n()) %>% 
  ungroup()

customers_2k_count_avg <- customers_2k_count %>% count(`Customer Name`) %>% 
  mutate(average_per_month = n / 12) %>% 
  arrange(desc(average_per_month))
  
```

#### Find number of orders per month that these customers place
```{r}
pi_over_2k <- customers_2k %>% 
  filter(Amount >= 2000, Canceled == 0)

orders_over_2k_per_month <- pi_over_2k %>%
  group_by(month = floor_date(`Posting Date`, "month")) %>%
  summarise(num_orders = n())

print(paste("2k Customers average orders per month = ", mean(orders_over_2k_per_month$num_orders)))
```

####Write to Excel File
```{r}
write_xlsx(customers_2k_count_avg, "Customers_Avg_Over_2k.xlsx")
```

